ITHIM Functions (BETA)

### 2019-08-07 ithim_r_function_descriptions.Rmd
Update ithim_r_function_descriptions.Rmd
A test push for trying pull request on a single file
documentation

---
title: "ITHIM Functions"
author: "Daniel Fuller"
date: '2018-10-22'
output: html_document
---

@@

### Common Abbreviations
- PA: Physical Activity
- AP: Air Pollution
- PM: Particulate Matter? 
- GDB: Global Burden of Disease
- HC: ??

>>>>

---
title: "ITHIM Functions (BETA)"
author: "Daniel Fuller"
date: '2018-10-22'
output: html_document
---

@@

### Common Abbreviations
- PA: Physical Activity
- AP: Air Pollution
- PM: Particulate Matter (PM2.5)
- GBD: Global Burden of Disease
- RR: Relative Risk
- DR: Dose Response
- PT: Public Transport
- mMET: marginal Metabolic Equivalent Task
- YLL: Years of Life Lost
